Robust receding horizon control for linear systems with state dependent disturbance

### 2015-04-21 draft_v2.tex
more edits section 5

\section{Controllable sets}\label{sec:preliminaries}
In this section we summarise results on controllable sets that allow the constraints of the problem~\eqref{eq:the:problem} to be to formulated
in a convenient way. The following result shows that the MRPI set (\ref{eq:definition:MRPI:set}) associated
with the pointwise polytopic set~\eqref{eq:PWA:def:disturbance} is polytopic if $H$ is elementwise convex and
piecewise affine. For a proof and detailed discussion of this result we refer the reader
to~\cite{Schaich:2015}.
%
\begin{lem}\label{thm:MRPI:set:is:polytopic}
Let $\mathcal X \subseteq \{x:\Gamma x\leq{\bf{1}}\wedge-\Gamma x\leq{\bf{1}}\}$ be polyhedral, and the pair $(A+BK,\Gamma)$ be
observable, furthermore let $\mathcal W(x,Kx)$ be defined as in~\eqref{eq:PWA:def:disturbance} with a elementwise convex piecewise
affine function $H(x,Kx)$ which is bounded for all finite $x$. Then the MRPI set $\mathcal X^\infty$ is a polytope, i.e.
it has the representation 
\begin{equation}\label{eq:halfspace:representation:MRPI}
	\mathcal X^\infty=\{x:\Lambda_i x\leq \lambda_i, \forall\, i\in\mathcal I^\infty\}.
\end{equation}
\end{lem}
%
We need to emphasise the following 
\begin{rem}\label{rem:vertex:representation}
Note that an essential assumption in Lemma~\ref{thm:MRPI:set:is:polytopic} is that $\mathcal W(x,u)$ is a polytope
for all finite $(x,u)$, i.e. it has a convex hull representation $\mathcal W(x,u) = \conv_k\{w_k(x,u)\}, k\in\{1,\dots,r\}$ where each 
vertex, $w_k(x,u)$, is a piecewise affine function of $(x,u)$, i.e.
\begin{multline}
	w_k(x,u) = \max\{W_{k,1}^x x + W_{k,1}^u u + w_{k,1}, \\
        W_{k,2}^x x + W_{k,2}^u u + w_{k,2},\dots\}
\end{multline}
where the maximisation is performed elementwise.
\end{rem}
%
We now derive the representation of $\mathcal Z_m$ and $\mathcal X_m$ as defined in~\eqref{eq:definition:stage:constraints}.
According to Lemma~\ref{thm:MRPI:set:is:polytopic} the MRPI set $\mathcal X^\infty$ is polytopic and has the 
representation~\eqref{eq:halfspace:representation:MRPI}. Therefore the recursion~\eqref{eq:definition:mixed:stage:constraint}
defines $\mathcal Z_1$ as
\begin{equation}\label{eq:derivation:of:mpLP:stage:constraints}
\begin{aligned}
	\mathcal Z_1 =& (\mathbb R^n\times\mathcal U)\cap 
\begin{aligned}[t] \Bigl\{(x,u): \Lambda_{0,i}(Ax&+Bu+Dw)\leq \lambda_{0,i} \\
& \forall w\in\mathcal W(x,u),\, i\in\mathcal I_0 \Bigr\} \end{aligned}
\\
	=&\begin{aligned}[t] (\mathbb R^n & \times \mathcal U) \cap\Bigl\{ (x,u): \\
& \max_{w\in\mathcal W(x,u)}\Lambda_{0,i}(Ax+Bu+Dw)\leq\lambda_{0,i},\, \forall i\in\mathcal I_0 \Bigr\} \end{aligned}
\\
	=&\begin{aligned}[t] & (\mathbb R^n \times\mathcal U)\cap \Bigl\{ (x,u): \\
& \!\!\!\!\!\!
\Lambda_{0,i}(Ax+Bu)+ \!\!\underbrace{\max_{j\in\{1,\dots,r\}}\Lambda_{0,i} Dw_j(x,u)}_{(i)}\leq\lambda_i, \, \forall i\in\mathcal I_0
	\Bigr\} \end{aligned}
\end{aligned}
\end{equation}
Since the maximisation $(i)$ in \eqref{eq:derivation:of:mpLP:stage:constraints} is a multi-parametric
linear program, its solution is piecewise affine in $(x,u)$. 
Therefore the set $\mathcal Z_1$ has a representation
$\mathcal Z_1=\{(x,u):\Xi^x_{1,i}x+\Xi^u_{1,i}u\leq\xi_{1,i},i\in\mathcal J_1\}$. The projection~$\mathcal X_1$ 
of $\mathcal Z_1$ onto~$\mathbb R^n$ is therefore has the representation~$\mathcal X_1 = \{x:\Lambda_{1,i} x\leq\lambda_{1,i},i\in\mathcal I_1\}$.
From here the determination of $\mathcal Z_k$ and $\mathcal X_k$ follows recursively. We are now able to formulate 
all constraints in~\eqref{eq:the:problem} as inequalities. In the next section we discuss a method of solving
min-max programs such as~\eqref{eq:the:problem} efficiently.

@@

In this section we apply the results derived in section~\ref{sec:gen:mpQP} to
the considered min-max robust control problem~\eqref{eq:the:problem}. We 
define a recursion and assume the active set is known to obtain a closed solution for~\eqref{eq:the:problem}.

@@

First epx

@@

with~$J_0^\ast(x^+) = \frac{1}{2}\norm{x^+}_P^2$ and $m=1,\dots,N$. Notice that explicitly using

@@

quadratic programs. Starting with the maximisation at stage $m=1$ and using a backward sweep approach (see e.g.~\cite{Bryson:1975}), 
we obtain

@@

    \max_{w,x^+} & -\frac{\gamma^2}{2}\norm{w}^2 + J_{m-1}^\ast(x^+)\\
    \text{s.t.} & \begin{array}{rcl}

@@

    \min_{u} & \frac{1}{2}\left(\norm{x}^2_Q + \norm{u}_R^2\right) + \hat J_m^\ast(x,u)\\
    \text{s.t.} & \begin{array}{ccccl}

@@

Since $J^\ast_0(x^+) = \frac{1}{2}\norm{x^+}_{P_0}^2$ is a given function, compatibility constraints are not necessary at 

@@

	\max_{w,x^+} & -\frac{\gamma^2}{2}\norm{w}^2 + J_{0}^\ast(x^+)\\

@@

be non-negative, i.e.~$\eta^\ast\geq0$. Notice that we omitted stage indices to avoid overloaded notation.

@@

\section{Exact solution of min-max program}\label{sec:line:search}
In the previous section we presented a recursive algorithm to solve~\eqref{eq:the:problem}
when all active constraints are known. In this section we present a method to find the active
constraints for a given initial state $\mathpzc x_e$ using a line search starting from a state $\mathpzc x_0$
for which the active constraints are known. In section~\ref{sec:gen:mpQP} and~\ref{sec:applied:mpQP}
we derived an explicit solution for each sub-optimisation program which depended affinely on the
state~$x$ at that stage~$m$ or the state and the input at that stage. Henceforth we denote the stage 
with an index, e.g.~$x_m$ denotes the optimised state in stage $m$, that is $x^{+,\ast}$ at stage $m+1$.
To ensure continuity of the dual variables we choose $\hat\zeta_m = \hat\beta_m$ and $\zeta_m=\beta_{m-1}$.
The affine character of the solution of each sub-problem allows us to parametrise the entire trajectory
with respect to parameters at stage~$m=N$, that is $x_N=\chi_0$ $x_N=\mathpzc x_0$ and $\beta_N$.

>>>>

\section{Controllable sets}\label{sec:preliminaries}
In this section we summarise results on controllable sets that allow the constraints of the problem~\eqref{eq:the:problem} to be to formulated
in a convenient way. The following result shows that the MRPI set (\ref{eq:definition:MRPI:set}) associated
with the pointwise polytopic set~\eqref{eq:PWA:def:disturbance} is polytopic if $H$ is elementwise convex and
piecewise affine. For a proof and detailed discussion of this result we refer the reader
to~\cite{Schaich:2015}.
%
\begin{lem}\label{thm:MRPI:set:is:polytopic}
Let $\mathcal X \subseteq \{x:\Gamma x\leq{\bf{1}}\wedge-\Gamma x\leq{\bf{1}}\}$ be polyhedral, and the pair $(A+BK,\Gamma)$ be
observable, furthermore let $\mathcal W(x,Kx)$ be defined as in~\eqref{eq:PWA:def:disturbance} with a elementwise convex piecewise
affine function $H(x,Kx)$ which is bounded for all finite $x$. Then the MRPI set $\mathcal X^\infty$ is a polytope, i.e.
it has the representation 
\begin{equation}\label{eq:halfspace:representation:MRPI}
	\mathcal X^\infty=\{x:\Lambda_i x\leq \lambda_i, \forall\, i\in\mathcal I^\infty\}.
\end{equation}
\end{lem}
%
We need to emphasise the following 
\begin{rem}\label{rem:vertex:representation}
Note that an essential assumption in Lemma~\ref{thm:MRPI:set:is:polytopic} is that $\mathcal W(x,u)$ is a polytope
for all finite $(x,u)$, i.e. it has a convex hull representation $\mathcal W(x,u) = \conv_k\{w_k(x,u)\}, k\in\{1,\dots,r\}$ where each 
vertex, $w_k(x,u)$, is a piecewise affine function of $(x,u)$, i.e.
\begin{multline}
	w_k(x,u) = \max\{W_{k,1}^x x + W_{k,1}^u u + w_{k,1}, \\
        W_{k,2}^x x + W_{k,2}^u u + w_{k,2},\dots\}
\end{multline}
where the maximisation is performed elementwise.
\end{rem}
%
We now derive the representation of $\mathcal Z_m$ and $\mathcal X_m$ as defined in~\eqref{eq:definition:stage:constraints}.
According to Lemma~\ref{thm:MRPI:set:is:polytopic} the MRPI set $\mathcal X^\infty$ is polytopic and has the 
representation~\eqref{eq:halfspace:representation:MRPI}. Therefore the recursion~\eqref{eq:definition:mixed:stage:constraint}
defines $\mathcal Z_1$ as
\begin{equation}\label{eq:derivation:of:mpLP:stage:constraints}
\begin{aligned}
	\mathcal Z_1 =& (\mathbb R^n\times\mathcal U)\cap 
\begin{aligned}[t] \Bigl\{(x,u): \Lambda_{0,i}(Ax&+Bu+Dw)\leq \lambda_{0,i} \\
& \forall w\in\mathcal W(x,u),\, i\in\mathcal I_0 \Bigr\} \end{aligned}
\\
	=&\begin{aligned}[t] (\mathbb R^n & \times \mathcal U) \cap\Bigl\{ (x,u): \\
& \max_{w\in\mathcal W(x,u)}\Lambda_{0,i}(Ax+Bu+Dw)\leq\lambda_{0,i},\, \forall i\in\mathcal I_0 \Bigr\} \end{aligned}
\\
	=&\begin{aligned}[t] & (\mathbb R^n \times\mathcal U)\cap \Bigl\{ (x,u): \\
& \!\!\!\!\!\!
\Lambda_{0,i}(Ax+Bu)+ \!\!\underbrace{\max_{j\in\{1,\dots,r\}}\!\Lambda_{0,i} Dw_j(x,u)}_{(i)}\leq\lambda_i, \, \forall i\in\mathcal I_0
	\Bigr\} \end{aligned}
\end{aligned}
\end{equation}
Since the maximisation $(i)$ in \eqref{eq:derivation:of:mpLP:stage:constraints} is a multi-parametric
linear program, its solution is piecewise affine in $(x,u)$. 
Therefore the set $\mathcal Z_1$ has a representation
$\mathcal Z_1=\{(x,u):\Xi^x_{1,i}x+\Xi^u_{1,i}u\leq\xi_{1,i},i\in\mathcal J_1\}$. The projection~$\mathcal X_1$ 
of $\mathcal Z_1$ onto~$\mathbb R^n$ is therefore has the representation~$\mathcal X_1 = \{x:\Lambda_{1,i} x\leq\lambda_{1,i},i\in\mathcal I_1\}$.
From here the determination of $\mathcal Z_k$ and $\mathcal X_k$ follows recursively. We are now able to formulate 
all constraints in~\eqref{eq:the:problem} as inequalities. In the next section we discuss a method of solving
min-max programs such as~\eqref{eq:the:problem} efficiently.

@@

In this section we apply the results derived in Section~\ref{sec:gen:mpQP} to the considered min-max robust
control problem~\eqref{eq:the:problem}. For the case that the set of active constraints is known, we define a
recursion that provides a closed solution for~\eqref{eq:the:problem}.

@@

We first express~\eqref{eq:the:problem} in the form

@@

with~$J_0^\ast(x^+) = \frac{1}{2}\|x^+\|_{P_0}^2$ and $m=1,\dots,N$. Notice that explicitly using

@@

quadratic programs. Starting with the maximisation at stage $m=1$ and using a backward sweep approach
\citep[see e.g.][]{Bryson:1975}, 
this yields

@@

    \max_{w,x^+}\ & {-\frac{\gamma^2}{2}}\norm{w}^2 + J_{m-1}^\ast(x^+)\\
    \text{s.t. }\  & \begin{array}[t]{rcl}

@@

    \min_{u}\ & \frac{1}{2}\left(\norm{x}^2_Q + \norm{u}_R^2\right) + \hat J_m^\ast(x,u)\\
    \text{s.t.}\ & \begin{array}[t]{ccccl}

@@

Given that $J^\ast_0(x^+) = \frac{1}{2}\|x^+\|_{P_0}^2$, compatibility constraints are not necessary at 

@@

	\max_{w,x^+} \ & {-\frac{\gamma^2}{2}}\norm{w}^2 + J_{0}^\ast(x^+)\\
	\text{s.t. }\ & 

@@

be non-negative, i.e.~$\eta^\ast\geq0$. Notice that we omit stage indices to avoid overloaded notation.

@@

\section{Exact solution of min-max program}\label{sec:line:search}
In the previous section we presented a recursive algorithm to solve~\eqref{eq:the:problem}
when all active constraints are known. In this section we present a method to find the active
constraints for a given initial state $\mathpzc x_e$ using a line search starting from a state $\mathpzc x_0$
for which the active constraints are known. In Section~\ref{sec:gen:mpQP} and~\ref{sec:applied:mpQP}
we derived an explicit solution for each sub-optimisation program which depended affinely on the
state~$x$ at that stage~$m$ or the state and the input at that stage. Henceforth we denote the stage 
with an index, e.g.~$x_m$ denotes the optimised state in stage $m$, that is $x^{+,\ast}$ at stage $m+1$.
To ensure continuity of the dual variables we choose $\hat\zeta_m = \hat\beta_m$ and $\zeta_m=\beta_{m-1}$.
The affine character of the solution of each sub-problem allows us to parametrise the entire trajectory
with respect to parameters at stage~$m=N$, that is $x_N=\chi_0$ $x_N=\mathpzc x_0$ and $\beta_N$.
